`r paste(params$city, params$state, sep = ', ')`

### 2017-11-30 lib/report.Rmd
progress
updates

Total rows: `r total_rows`

```{r by_incident_type_table}
by_incident_type_table
```

@@

>>>>

\begin{center}
`r prettyNum(total_rows, big.mark = ",")` rows

`r date_range[1]` to `r date_range[2]`
\end{center}

```{r by_incident_type_table, fig.align = 'left'}
by_incident_type_table
```

```{r null_rates_table}
null_rates_table
```

@@

```{r by_year_by_day_plot, fig.height = 10}
by_year_by_day_plot
```

```{r race_pct_plot}
race_pct_plot
```
